Hypertension and microbiome

### 2019-04-25 articletwo.Rmd
Bug
Minor

```{r maaslin runs, results = 'hide'} 
maaslin <- list()
lm (Sutterella_Bacteria ~ MAP + BL_AGE + SEX + BMI + CURR_SMOKE + Q57X + DIAB + BL_USE_RX_C03 + 
                           BL_USE_RX_C07 + BL_USE_RX_C08 + BL_USE_RX_C09, )

@@

@@

tbl2 <- flextable(data = maaslin.lacto.max.table) %>%
    set_header_df(mapping = typology.tbl2, key = "col_keys") %>%
        flextable::theme_booktabs()
writetable(doc, tbl2, number = 2, tbl2head, tbl2foot)
print(doc, target = paste0("report/articletwo-test.docx"))
```

>>>>

```{r maaslin runs, results = 'hide'} 
maaslin <- list()

@@

```{r salt}
lacto.meta <- meta(pseq.genus) %>%
    tibble::rownames_to_column("id")

lacto.abund <- subset_taxa(pseq.genus, Genus=="Lactobacillus") %>%
    abundances(., transform = "clr") %>%
    t %>%
    as.data.frame %>%
    tibble::rownames_to_column("id") %>%
    setNames(tolower(replace.brackets(names(.))))

lacto.full <- full_join(lacto.meta, lacto.abund, by = "id") %>%
    dplyr::mutate(fake_salt = relevel(factor(dplyr::ntile(BL_AGE, 4)), ref='1'),
                  lacto_groups = relevel(factor(dplyr::ntile(lactobacillus.bacteria, 4)), ref='1'))

lacto.mean <- lacto.full %>%
    group_by(fake_salt) %>%
    summarize(estimate = t.test(lactobacillus.bacteria)$"estimate",
              qi_low = t.test(lactobacillus.bacteria)$"conf.int"[1],
              qi_high = t.test(lactobacillus.bacteria)$"conf.int"[2],
              group = "mean")

lacto.odds <- lacto.full %>%
    group_by(lacto_groups) %>%
    do(oddsmodel = glm(HYPERTENSION ~ lactobacillus.bacteria, family=binomial(link="logit"), data = .)) %>%
    do(data.frame(
        fake_salt = .$lacto_groups,
        term = names(coef(.$oddsmodel)),
        exp(cbind(coef(.$oddsmodel), confint(.$oddsmodel))))) %>%
    dplyr::mutate(group = "odds") %>%
    dplyr::rename(estimate = V1, qi_low = X2.5.., qi_high = X97.5..) %>%
    filter(!grepl("Intercept", term)) %>%
    select(-term)
```

```{r forest plot lacto, eval = FALSE}

myforestplot <- function(data) {
    ggplot(data = data,
           aes(x = fake_salt, y = estimate, ymin = qi_low, ymax = qi_high)) +
        facet_wrap(~group,strip.position="top",nrow=1,scales = "free_y") +
        xlab('Group') +
        ylab("Risk Ratio (95% Confidence Interval)")+
        geom_pointrange()+
        geom_hline(aes(fill=fake_salt), yintercept=1, linetype=2)+
        geom_errorbar(aes(ymin=qi_low, ymax=qi_high),width=0.2,cex=1)+ 
        theme(plot.title=element_text(size=16,face="bold"),
              axis.text.x=element_text(face="bold"),
              axis.title=element_text(size=12,face="bold"),
              strip.background = element_blank(),
              strip.placement = "outside") + 
        ggplot2::theme_minimal() 
}

gsalt <- grid.arrange(myforestplot(lacto.mean),  myforestplot(lacto.odds), ncol=2)
ggsave(file = "cache/salt-forest.png", plot=gsalt, height=6, width=9)
```

@@

tbl2 <- flextable(data = maaslin.lacto.max.table) %>%
    set_header_df(mapping = typology.tbl2, key = "col_keys") %>%
        flextable::theme_booktabs()
```
